Data Preparation

### 2024-04-12 data_prep.Rmd
deleting large files

---
title: "Who needs privacy? Exploring the relations between need for privacy and personality"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

@@

knitr::opts_chunk$set(
  warning=F, 
  echo=F, 
  error=F, 
  message=F, 
  cache = T, 
  tidy=T, 
  dev = 'pdf', 
  cache.extra = knitr::rand_seed
  )

@@

Here you can find the results of our study.

# Set-Up
## Packages

```{r r-setup, include=T, echo=T, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

library(confintr)
library(corrplot)
library(devtools)
library(easystats)
library(GGally)
library(ggplot2)
library(haven)
library(kableExtra)
library(knitr)
library(lavaan)
library(magrittr)
library(mice)
library(MVN)
library(naniar)
library(PerFit)
library(psych)
library(quanteda.textstats)
library(pwr)
library(semPlot)
library(sjlabelled)
library(simsem)
library(semTools)
library(tidyverse)
library(td)

@@

```{r data-wrangling}
# d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
d_raw <- sjlabelled::read_spss(
  "data/Need+for+Privacy_February+6%2C+2024_15.56.sav",
  convert.factors = FALSE
  )
```

### Data-Wrangling

@@

d <-
  d_raw %>% 
  rename(
    COL = COL_,
    REL = REL_
    ) %>%
  mutate(
    across(all_of(vars_invert),
    ~ 8 - .x
         ),
    male = case_match(
      GEN,
      c(2, 3) ~ 0,
      1 ~ 1),
    age = case_match(
      AGE,
      1 ~ 1,
      2 ~ 2,
      3 ~ 3,
      4 ~ 4,
      5 ~ 7,
      6 ~ 5,
      7 ~ 6),
    white = case_match(
      ETH,
      2 ~ 0,
      1 ~ 1),
    relation = case_match(
      REL,
      2 ~ 1,
      1 ~ 0),
    college = case_match(
      COL,
      2 ~ 1,
      1 ~ 0),
    conserv = CON,
    income = INC
  ) 
```

### Labels

```{r data-labels}
# define vars and labels
vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")
vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")

vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
                   "HEX_ALT",
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Altruism",
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality")

vars_pers_hoh <- 
  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")
vars_pers_emo <- 
  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")
vars_pers_ext <- 
  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")
vars_pers_agr <- 
  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")
vars_pers_cns <- 
  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")
vars_pers_opn <- 
  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

@@

vars_pers_all_txt <- 
  c("Honesty humility", 
      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
    "Emotionality", 
      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
    "Extraversion",
      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
    "Agreeableness",
      "Forgiveness", "Gentleness", "Flexibility", "Patience",
    "Conscientiousness",
      "Organization", "Diligence", "Perfectionism", "Prudence", 
    "Openness",
      "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
    )

@@

vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")
vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
                       "Agreeableness", "Conscientiousness", "Openness")

vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Psychological", "Social", "Physical", 
                  "Government", "Companies", 
                  "Informational", "Anonymity", "General")
vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
                  "Govern-\nment", "Companies", 
                  "Infor-\nmational", "Anony-\nmity", "General")
vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
                  "Gov.", "Comp.", 
                  "Inform.", "Anonym.", "General")

vars_pers_pri <- c(vars_pers_fac, vars_pri)
```

@@

```{r}
# Person means per facet

d %<>%
  mutate(
    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
  )

@@

# Missing data

First filter those who didn't finish the questionnaire.

@@

```{r}
n_miss(d)
prop_miss(d)
```

Only 23 cells are missing -- which is very little. To be precise, 0.00006 percent only.

@@

```{r}
miss_var_summary(d) %>% 
  head(19)
```

@@

```{r}
miss_case_summary(d)
```

@@

# Quality checks

@@

However, this made little sense. The median response time was `r time_med` and the standard deviation `r time_sd`. Hence, three SDs below median was `r time_crit_init`, hence not informative.

@@

Let's inspect for potential response patterns.

# Sociodemographics

To improve privacy, we didn't collect exact but binned measures of sociodemographics.

Let's first inspect age. Here, the age categories were as follows:

1: Under 18 years old
2: 18-24 years old 
3: 25-34 years old 
4: 35-44 years old 
5: 45-54 years old 
6: 55-64 years old 
7: 65+ years old

```{r}
table(d$AGE)
```

No person indicated being younger than 18 years old. Hence, everybody could be included.

```{r}
age_m <- 
  mean(d$AGE)
```

The mean age was 45 to 54 years of age.

Let's next inspect gender. Categories were:

1: "Man" 
2: "Woman" 
3: "Third gender / Other"

```{r}
table(d$GEN) %>% 
  prop.table() %>% 
  round(2)
```

48 percent were male, 50 female, and 1 percent indicated third/other gender.

Let's next inspect education. Categories were:

1: "No college degree" 
2: "College degree"

```{r}
table(d$COL) %>% 
  prop.table() %>% 
  round(2)
```

69% reported having a college degree.

Let's next inspect ethnicity. Answer categories were as follows:

1: "White"
2: "Other"

```{r}
table(d$ETH) %>%
  prop.table() %>% 
  round(2)
```

78 % percent were white, 22 % not white.

# Items

All items were answered on a 7-point scale with the following options:

"To what extent do you agree or disagree with the following statements?"

(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree

## Ceiling/Floor effects

Let's first check for ceiling and floor effects.

```{r}
d %>%
  select(
    paste0(rep(vars_pers_pri, each = 4), "_0", 1:4)
  ) %>% 
  apply(
    2,  mean, na.rm = T
  )
```

No item below floor (1.5) or ceiling (6.5) thresholds.

## Personality
### Honesty Humility
#### Sincerity

 - If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
 - I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
 - If I want something from someone, I will laugh at that person's worst jokes.
 - I wouldn't pretend to like someone just to get that person to do favors for me.

```{r}
name <- "HEX_HOH_SIN"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}
model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is okay, but RMSEA is significantly above .10. Let's hence inspect modification indices to see if there are potential fixes.

```{r}
modindices(fit_HEX_HOH_SIN)
```

Suggests that item 1 & 3, and item 2 & 4 build subdimensions. Let's allow covariances.

```{r}
model <- 
  "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
  HEX_HOH_SIN_01 ~~ a*HEX_HOH_SIN_03
  HEX_HOH_SIN_02 ~~ a*HEX_HOH_SIN_04
"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is now great.

#### Fairness

 - If I knew that I could never get caught, I would be willing to steal a million dollars.
 - I would be tempted to buy stolen property if I were financially tight.
 - I would never accept a bribe, even if it were very large.
 - I’d be tempted to use counterfeit money, if I were sure I could get away with it.

```{r}
name <- "HEX_HOH_FAI"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}

model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is good.

#### Greed Avoidance

 - Having a lot of money is not especially important to me.
 - I would like to live in a very expensive, high-class neighborhood.
 - I would like to be seen driving around in a very expensive car.
 - I would get a lot of pleasure from owning expensive luxury goods.

```{r}
name <- "HEX_HOH_GRE"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}

model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is okaish, but RMSEA above .10. Let's inspect modification indices.

```{r}
modindices(fit_HEX_HOH_GRE)
```

Item 1 & 2, and item 3 & 4 form subdimensions.

```{r}
model <- "
  HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
  HEX_HOH_GRE_01 ~~ a*HEX_HOH_GRE_02
  HEX_HOH_GRE_03 ~~ a*HEX_HOH_GRE_04
"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is now great.

#### Modesty

 - I am an ordinary person who is no better than others.
 - I wouldn’t want people to treat me as though I were superior to them.
 - I think that I am entitled to more respect than the average person is.
 - I want people to know that I am an important person of high status.

```{r}
name <- "HEX_HOH_MOD"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}
model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is good.

#### Honesty Humility

Let's also look at the dimension itself.

```{r}
model_hex_hoh <- "
# Personality Factors
HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04

# Covariances
HEX_HOH_SIN_01 ~~ HEX_HOH_SIN_03
HEX_HOH_SIN_02 ~~ HEX_HOH_SIN_04
HEX_HOH_GRE_01 ~~ HEX_HOH_GRE_02
HEX_HOH_GRE_03 ~~ HEX_HOH_GRE_04
"
fit_hex_hoh <- sem(model_hex_hoh, d, estimator = "MLM", fixed.x = TRUE)
summary(fit_hex_hoh, standardized = TRUE, fit = TRUE)
```

### Emotionality
#### Fearfulness

 - I would feel afraid if I had to travel in bad weather conditions.
 - I don’t mind doing jobs that involve dangerous work.
 - When it comes to physical danger, I am very fearful.
 - Even in an emergency I wouldn't feel like panicking.

```{r}
name <- "HEX_EMO_FEA"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}
model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLR", missing = "FIML")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is great.

#### Anxiety

 - I sometimes can't help worrying about little things.
 - I worry a lot less than most people do.
 - I rarely, if ever, have trouble sleeping due to stress or anxiety.
 - I get very anxious when waiting to hear about an important decision.

```{r}
name <- "HEX_EMO_ANX"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}

model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is great.

#### Dependence

 - When I suffer from a painful experience, I need someone to make me feel comfortable.
 - I can handle difficult situations without needing emotional support from anyone else.
 - Whenever I feel worried about something, I want to share my concern with another person.
 - I rarely discuss my problems with other people.

```{r}
name <- "HEX_EMO_DEP"

plot_hist(name)

>>>>

---
title: "Data Preparation"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: show
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

@@

knitr::opts_chunk$set(
  warning=F, 
  echo=T, 
  error=F, 
  message=F, 
  cache = T, 
  tidy=T, 
  dev = 'pdf', 
  cache.extra = knitr::rand_seed,
  fig.height = 6,
  fig.width = 8
  )

@@

Here we outline how we prepared the data for our analyses, including quality checks.

# Data

Please first download the data from [AUSSDA](https://data.aussda.at/dataset.xhtml?persistentId=doi:10.11587/IC66GC) and put it into the folder "data".

# Set-up

We load the packages.

```{r r-setup, include=T, echo=T, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

library(confintr)
library(corrplot)
library(easystats)
library(ggplot2)
library(kableExtra)
library(knitr)
library(lavaan)
library(magrittr)
library(MVN)
library(naniar)
library(PerFit)
library(psych)
library(sjlabelled)
library(semTools)
library(tidyverse)
library(td)

@@

We next load the data.

```{r data-wrangling}
d_raw <- sjlabelled::read_spss(
  "data/10849_da_en_v1_0.zsav",
  convert.factors = FALSE
  )
```

# Data Preparation

## Recoding

We need to recode inverted items, rename variables, and recode variables (Age was coded wrongly).

@@

d <-
  d_raw %>% 
  rename(
    COL = COL_,
    REL = REL_
    ) %>%
  mutate(
    across(all_of(vars_invert),
    ~ 8 - .x
         ),
    male = case_match(
      GEN,
      c(2, 3) ~ 0,
      1 ~ 1),
    # note that age was coded wrongly; needs to be corrected
    age = case_match(
      AGE,
      1 ~ 1,
      2 ~ 2,
      3 ~ 3,
      4 ~ 4,
      5 ~ 6,
      6 ~ 7,
      7 ~ 5),
    age = set_labels(
      age, 
      labels = c(
        "18-24 years old", 
        "25-34 years old", 
        "35-44 years old", 
        "45-54 years old",
        "55-64 years old", 
        "65+ years old"
      )
    ),
    white = case_match(
      ETH,
      2 ~ 0,
      1 ~ 1),
    relation = case_match(
      REL,
      2 ~ 1,
      1 ~ 0),
    college = case_match(
      COL,
      2 ~ 1,
      1 ~ 0),
    conserv = CON,
    income = INC
  ) 
```

## Labels

We define names and labels for categories of variables, so that we can use them later.

```{r data-labels}
# define vars and labels
vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")

vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")

vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
                   "HEX_ALT",
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Altruism",
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesth. appreciation", "Inquisitiveness", "Creativeness", "Unconventionality")

vars_pers_hoh <- 
  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")

vars_pers_emo <- 
  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")

vars_pers_ext <- 
  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")

vars_pers_agr <- 
  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")

vars_pers_cns <- 
  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")

vars_pers_opn <- 
  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

@@

vars_pers_all_txt <- 
  c("Honesty humility", 
      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
    "Emotionality", 
      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
    "Extraversion",
      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
    "Agreeableness",
      "Forgiveness", "Gentleness", "Flexibility", "Patience",
    "Conscientiousness",
      "Organization", "Diligence", "Perfectionism", "Prudence", 
    "Openness",
      "Aesth. appreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
    )

@@

vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")

vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
                       "Agreeableness", "Conscientiousness", "Openness")

vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")

vars_pri_txt <- c("Psychological", "Social", "Physical", 
                  "Government", "Companies", 
                  "Informational", "Anonymity", "General")

vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
                  "Govern-\nment", "Companies", 
                  "Infor-\nmational", "Anony-\nmity", "General")

vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
                  "Gov.", "Comp.", 
                  "Inform.", "Anonym.", "General")

vars_pers_pri <- c(vars_pers_fac, vars_pri)

vars_all <- c(
  vars_pers_all, 
  vars_pri,
  vars_ses
)
```

@@

Below we compute the means for scales and items.

```{r}
# Person means per facet
d %<>%
  mutate(
    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
  )

@@

# Quality checks
## Missing data

First we filter those who didn't finish the questionnaire.

@@

```{r}
missing_n <- 
  d %>% 
  select(HEX_HOH_SIN_01:CON) %>% 
  n_miss()

missing_per <- 
  d %>% 
  select(HEX_HOH_SIN_01:CON) %>%
  prop_miss() %>% 
  as.numeric() * 100
```

Only `r missing_n` cells are missing -- which is very little. To be precise, `r missing_per %>% round(4)` percent only.

@@

```{r}
d %>% 
  select(HEX_HOH_SIN_01:CON) %>% 
  miss_var_summary() %>% 
  head(19)
```

@@

```{r}
d %>% 
  select(HEX_HOH_SIN_01:CON) %>% 
  miss_case_summary()
```

@@

## Speeders

@@

However, this made little sense. The median response time was `r time_med` seconds and the standard deviation `r time_sd %>% round(0)` seconds. Hence, three SDs below median was `r time_crit_init %>% round(0)` seconds, hence not informative.

@@

## Response patterns

Let's inspect for potential response patterns. We'll do so looking at influential cases, which we'll then inspect manually.

We'll use raw data, so that inverted items aren't recoded and patterns become more visible. (Note that this data set isn't yet filtered for speeders).

```{r}
options(mc.cores = 8)

# analyses require complete cases only
d_raw_compl <- d_raw %>% 
  select(ID, Duration__in_seconds_, HEX_HOH_SIN_01:PRI_BEH) %>% 
  .[complete.cases(.), ]

outliers <- 
  check_outliers(
    d_raw_compl, 
    method = "all", 
    verbose = FALSE
  )

summary(outliers)
```

194 outliers were detected. We'll now inspect these outliers manually.

```{r}
d_outliers_stats <- as.data.frame(outliers)

d_outliers <- 
  d_raw_compl[d_outliers_stats$Outlier >= 0.5, ] %>%
  as.data.frame()

d_outliers

patterns <- c(
  449      # "R_72Kshi80pwPq9Gy"
  , 6      # "R_5OrhZQwvj9wfJWp"
  , 705    # "R_5QSPlArm0BtfIrE"
  , 1422   # "R_3Cv1Tmj5HX4ghJU"
  , 1401   # "R_5Pld7hbh1ay8sb7"
  , 1355   # "R_4DuqyujkQ7Hjapj"
  , 273    # "R_6MqzefRkB3aQdPj"
  , 747    # "R_7QSq0FbgZfcnJIt"
  , 1406   # "R_1MrHTg5CZpBLeYw"
  )
```

The following `r length(patterns) %>% english::english()` cases show clear patterns and will be removed.

```{r}
d_filtered <- filter(d, ID %in% patterns)
d_filtered

d <- filter(d, !ID %in% patterns)
n_final <- nrow(d)
```
